---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# hlidacr

<!-- badges: start -->
[![R build status](https://github.com/skvrnami/hlidacr/workflows/R-CMD-check/badge.svg)](https://github.com/skvrnami/hlidacr/actions)
[![codecov](https://codecov.io/gh/skvrnami/hlidacr/branch/main/graph/badge.svg?token=FWP73F1DOL)](https://codecov.io/gh/skvrnami/hlidacr)
<!-- badges: end -->

The goal of hlidacr is to provide access to the data published by [Hlídač státu](https://www.hlidacstatu.cz/) provided by their [API](https://www.hlidacstatu.cz/api/v2/swagger/index). 

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("skvrnami/hlidacr")
```

Besides the installation, you need access token for making API requests. 
The access token is available [here](https://www.hlidacstatu.cz/api/v1/Index) 
after the registration at the Hlídač státu's website. 

## Usage

The package implements functions for accessing all publicly available API endpoints
as defined in the [documentation](https://www.hlidacstatu.cz/api/v2/swagger/index)
of the Hlídač státu API. 

The data available via the API are related to:  
- funding of political parties
- transcriptions of parliamentary speeches
- contracts between public institutions and private companies
- availability of websites operated by public institutions
etc.

This is a basic example which shows you how to solve a common problem:

```{r example}
library(hlidacr)

# Authorization token
TOKEN <- Sys.getenv("HLIDAC_TOKEN")

datasets <- get_datasets(TOKEN)
str(datasets, max.level = 1)

head(datasets$Results[,1:2], 10)
```

